R for Clinical Study Reports and Submission

### 2021-11-10 preface.Rmd
clarify license; optimize contributor display

# Introduction {#intro}

@@

In addition, R package folder structure is also recommended
to develop Shiny apps as discussed
in [Chapter 20 of the Master Shiny book](https://mastering-shiny.org/scaling-packaging.html)
and the [Engineering Production-Grade Shiny Apps](https://engineering-shiny.org/golem.html) book.

@@

- Part 2, "Clinical trial project" provides general information
  with examples to manage a clinical trial A&R project.
  In this part, we assume a reader is a project lead with experience in R package development.
  Some good references include [R Packages](https://r-pkgs.org/) and
  [The tidyverse style guide](https://style.tidyverse.org/).

@@

We share the same philosophy described in
[Section 1.1 of the R Packages book](https://r-pkgs.org/intro.html#intro-phil)
and quote here.

@@

>>>>

# Preface {-}

@@

In addition, R package folder structure is also recommended
to develop Shiny apps as discussed
in Chapter 20 of the [Mastering Shiny](https://mastering-shiny.org/scaling-packaging.html) book
and the [Engineering Production-Grade Shiny Apps](https://engineering-shiny.org/golem.html) book.

@@

- Part 2, "Clinical trial project" provides general information
  with examples to manage a clinical trial A&R project.
  In this part, we assume a reader is a project lead with experience in R package development.
  Some good references include [R Packages](https://r-pkgs.org/) and the
  [tidyverse style guide](https://style.tidyverse.org/).

@@

We share the same philosophy described in
Section 1.1 of the [R Packages](https://r-pkgs.org/intro.html#intro-phil) book
and quote here.

@@

## Authors and contributors

The document is maintained by a community.
While reading the document, you can be a contributor as well.
The quality of this document relies on you.

- Authors: contributed the majority of content to at least one chapter.

  Yilong Zhang <<yilong.zhang@merck.com>>, Nan Xiao, Keaven Anderson

- Contributors: contributed at least one commit to the [source code](https://github.com/elong0527/r4csr).

```{r, results = "asis", echo = FALSE, message = FALSE}
contributors <- read.csv("contributors.csv", stringsAsFactors = FALSE, na.strings = "")
contributors$desc <- with(contributors, ifelse(is.na(username), name, paste0(name, " (\\@", username, ")")))
cat("  We are grateful for all the improvements brought by these contributors (in chronological order): ", sep = "")
cat(paste0(contributors$desc, collapse = ", "))
cat(".\n")
```
